% Auto-generated bibliography (ASCII-safe)
\begin{thebibliography}{99}
\bibitem{Ankner2024Hydra} Philipp Ankner, et al. Hydra: Sequential Multi-Head Speculative Decoding. 2024. Preprint.
\bibitem{BanerjeeKendall2016Rigidity} Sayan Banerjee and Wilfrid S. Kendall. Rigidity for Markovian maximal couplings. Electronic Communications in Probability, 21:1--12, 2016.
\bibitem{Boettcher2017MMC} Jan M. Böettcher. On Markovian Maximal Couplings. Journal of Applied Probability, 54(4):1137--1150, 2017.
\bibitem{Chen2024Sequoia} Zihan Chen, et al. Sequoia: Scalable and Efficient Speculative Decoding. 2024. Preprint.
\bibitem{DraftVerifyACL2024} Author(s) omitted. Draft-Verify: Fast and Accurate LLM Inference with Draft-Verify. In Proceedings of ACL, 2024.
\bibitem{Fu2024Lookahead} Yaru Fu, et al. Lookahead Decoding for Large Language Models. 2024. Preprint.
\bibitem{Leviathan2023SpeculativeDecoding} Yaniv Leviathan, Matan Kalman, and Yossi Matias. Fast Inference from Transformers via Speculative Decoding. In Proceedings of the 40th International Conference on Machine Learning (ICML), Proceedings of Machine Learning Research, volume 202, pages 19274--19286, 2023. \url{https://proceedings.mlr.press/v202/leviathan23a.html}
\bibitem{Xia2022SpeculativeDecoding} Heming Xia, Tao Ge, Peiyi Wang, Si-Qing Chen, Furu Wei, and Zhifang Sui. Speculative Decoding: Exploiting Speculative Execution for Accelerating Seq2seq Generation. arXiv preprint arXiv:2203.16487, 2022. \url{https://doi.org/10.48550/arXiv.2203.16487}
\bibitem{ShakedShanthikumar2007StochasticOrders} Moshe Shaked and J. George Shanthikumar. Stochastic Orders. Springer Series in Statistics. Springer, New York, 2007. \url{https://doi.org/10.1007/978-0-387-34675-5}
\bibitem{Lindvall2002CouplingMethod} Torgny Lindvall. Lectures on the Coupling Method. Dover Publications, Mineola, NY, 2002 (reprint of the 1992 Wiley edition). \url{https://books.google.com/books?id=GUwyU1ypd1wC}
\bibitem{Naudts2009QExponentialFamily} Jan Naudts. The q-exponential family in statistical physics. Open Physics, 7(1):130--145, 2009. \url{https://doi.org/10.2478/s11534-008-0150-x}
\bibitem{Miao2023SpecInfer} Haotian Miao, et al. SpecInfer: Accelerating Large Language Model Inference via Speculative Decoding. 2023. Preprint.
\bibitem{Mamou2024DISCO} Jonathan Mamou, et al. DISCO: Dynamic Speculation for Efficient Decoding. 2024. Preprint.
\bibitem{Sun2023SpecTr} Shuo Sun, et al. SpecTr: Speculative Decoding via Optimal Transport. 2023. Preprint.
\bibitem{Sun2024BlockVerification} Shuo Sun, et al. Blockwise Verification for Speculative Decoding. 2024. OpenReview preprint. \url{https://openreview.net/pdf?id=OWwc8eOIm8}
\bibitem{Xia2024Survey} Heming Xia, et al. Speculative Decoding for Large Language Models: A Survey. 2024. Preprint.
\end{thebibliography}
