\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1.1in}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathtools}
\usepackage{amscd}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=magenta, urlcolor=blue}
\usepackage{enumitem}

% Relax line-breaking to avoid overfull boxes in math-heavy prose
\setlength{\emergencystretch}{3em}

% Consolidated macros (each defined exactly once)
\newcommand{\Sp}{\operatorname{Sp}}
\newcommand{\IndCoh}{\mathrm{IndCoh}}
\newcommand{\Nilp}{\mathrm{Nilp}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\Shv}{\mathrm{Shv}}
\newcommand{\Bun}{\mathrm{Bun}}
\newcommand{\QCoh}{\mathrm{QCoh}}
\newcommand{\restr}{\mathrm{restr}}
\newcommand{\coarse}{\mathrm{coarse}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cC}{\mathcal{C}}
% Soft-break composition operator for long functor chains
\newcommand{\ccomp}{\mathrel{\mkern2mu\circ\mkern2mu}\allowbreak}
% Lightweight placeholders used in statements when inputs are commented
\newcommand{\Vac}{\mathrm{Vac}}
\newcommand{\Poinc}{\mathrm{Poinc}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\coeff}{\mathrm{coeff}}

% Theorem environments (support nested lemmas via proof titles)
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% Title and metadata
\title{Specialization, Parabolic Zastava, and Coarse Spectral Functoriality in Geometric Langlands}
\author{\small Anonymous}
\date{\small September 27, 2025}

\begin{document}
\maketitle

\begin{abstract}
We study specialization phenomena and functorial compatibilities at both the automorphic and spectral sides of the geometric Langlands program over a discrete valuation ring $R_0$ with fraction field $K$ and residue field $k$. Our main contributions are: (i) commutativity of specialization with the coarse restricted Langlands functor on nilpotent-supported sheaves; (ii) flatness and universally locally acyclic (ULA) behavior for parabolic Zastava kernels in families over $\operatorname{Spec} R_0$ and a corresponding identity for vacuum Whittaker coefficients; (iii) a scheme-theoretic description of spectral support generated by Hecke orbits and conservativity of the coarse spectral functor on tempered objects; (iv) a QCoh-valued spectral specialization formula compatible with Hecke and Eisenstein functors; (v) essential surjectivity of specialization on the spectral $\IndCoh_{\Nilp}$-side in mixed characteristic; (vi) compatibility of specialization with support and an equality of categorical Frobenius traces after restricting to nilpotent singular support. Together these results give a coherent picture of how Hecke dynamics, Eisenstein series, and Whittaker coefficients behave under specialization and under the passage from sheaf-theoretic to coarse spectral data.
\end{abstract}

\tableofcontents

\section{Introduction}
A guiding theme in geometric Langlands is the interaction between automorphic categories on $\Bun_G$ and spectral categories of sheaves on stacks of (restricted) $\check G$-local systems $\LS^{\restr}_{\check G}$. On the spectral side, nilpotent singular support \cite{ArinkinGaitsgory2015-SingularSupport} plays a central role, while on the automorphic side, the geometry of Drinfeld compactifications and Zastava spaces controls Eisenstein series \cite{BravermanGaitsgory2002-GeometricEisenstein,BFGM2002-ICDrinfeld}. The framework of restricted local systems \cite{AGKRRV2020-RestrictedLocSys} provides a sheaf-theoretic incarnation that is robust across sheaf theories. Recent advances toward, and culminating in, the construction of the global Langlands functor in characteristic zero \cite{GaitsgoryRaskin2024-GLFunctorI} motivate a closer analysis of specialization and base change phenomena at both sides.

In this paper, we develop a family of results organized around specialization from $K$ to $k$ and around the coarse (QCoh-valued) avatar of the Langlands functor. We show that the coarse functor commutes with specialization, that parabolic Zastava kernels are flat and ULA in families, that Hecke orbits control spectral support for tempered objects and force conservativity of the coarse functor, and that spectral specialization has a concrete QCoh-valued description compatible with Hecke and Eisenstein operations. We further prove essential surjectivity of the spectral specialization functor in mixed characteristic and compatibility of supports under specialization, and we identify categorical Frobenius traces after imposing nilpotent singular support.

\subsection*{Organization}
Section\ \ref{sec:setup} recalls notation and basic constructions. Section\ \ref{sec:main} states our main results, inserted via \verb+\input+ from the companion files. Section\ \ref{sec:applications} explains consequences for supports, Hecke dynamics, Eisenstein series, and Whittaker coefficients. Section\ \ref{sec:related} situates our results within the literature. We conclude with a summary and outlook.

\section{Notation and setup}\label{sec:setup}
Throughout, $R_0$ is a discrete valuation ring with fraction field $K$ and residue field $k$. We write $\Bun_{G,(-)}$ for the stack of $G$-bundles over the base curve after extension of scalars to $(-)\in\{K,k\}$ (or to $R_0$ when indicated). We work with a sheaf theory $\Shv$ (e.g., $\ell$-adic) and denote by $\Shv_{\Nilp}(\Bun_{G,(-)})$ the full subcategory with nilpotent singular support on the automorphic side. On the spectral side, $\LS^{\restr}_{\check G,(-)}$ denotes the stack of restricted local systems \cite{AGKRRV2020-RestrictedLocSys}; we use both $\QCoh(\LS^{\restr}_{\check G,(-)})$ and $\IndCoh_{\Nilp}(\LS^{\restr}_{\check G,(-)})$ as needed.

We use $\Sp_{K\to k}$ for (sheaf-theoretic) specialization and $\Sp^{\QCoh}_{K\to k}$ and $\Sp^{\IndCoh}_{K\to k}$ for its spectral counterparts on QCoh and IndCoh, respectively. For a standard parabolic $P^-\subset G$ with Levi $M$, we write $\mathrm{Eis}^-_{!}$ for the !-Eisenstein series functor constructed with the parabolic Zastava kernel, and $\mathrm{coeff}^{\Vac}$ for the vacuum Whittaker coefficient. We denote by $\mathsf L^{\restr}_{G,\coarse}$ the QCoh-valued coarse Langlands functor.

\section{Main results}\label{sec:main}
We now state the main theorems in a form optimized for use later in the paper. Each statement is inserted from a separate file.

\subsection{Specialization and the coarse Langlands functor}
Our first result identifies specialization with derived base change at the coarse level and proves essential surjectivity of specialization on the spectral IndCoh side in mixed characteristic.

\begin{theorem}[Commutativity with coarse restriction] \label{thm:intro:coarse-specialization}
See Theorem~\ref{thm:langlands-specialization}.
\end{theorem}

\input{thm_langlands-specialization.tex}

\subsection{Parabolic Zastava in families: flatness, ULA, and Whittaker coefficients}
The next result establishes flatness and ULA properties for the parabolic Zastava kernel over families and deduces a base-change-compatible formula for vacuum Whittaker coefficients.

\begin{theorem}[Parabolic Zastava over $R_0$] \label{thm:intro:zastava}
See Theorem~\ref{thm:parabolic-zastava-flatness}.
\end{theorem}

\input{thm_parabolic-zastava-flatness.tex}

\subsection{Hecke orbits and coarse spectral support}
We relate the scheme-theoretic spectral support of the coarse image to the Hecke orbit of a tempered automorphic object and deduce conservativity.

\begin{theorem}[Hecke orbit control and conservativity] \label{thm:intro:hecke}
See Theorem~\ref{thm:hecke-orbit-support}.
\end{theorem}

\input{thm_hecke-orbit-support.tex}

\subsection{QCoh-valued spectral specialization}
We provide an explicit QCoh-valued spectral specialization formula, compatible with Hecke and Eisenstein functors, recovering a Whittaker coefficient identity upon taking global sections.

\begin{theorem}[QCoh-level spectral specialization] \label{thm:intro:spectral-qcoh}
See Theorem~\ref{thm:spectral-specialization}.
\end{theorem}

\input{thm_spectral-specialization.tex}

\subsection{Specialization of supports}
We identify the behavior of spectral supports under specialization.

\begin{proposition}[Specialization of spectral supports] \label{prop:intro:supp}
See Proposition~\ref{prop:supp-specialization}.
\end{proposition}

\input{prop_supp-specialization.tex}

\subsection{Frobenius traces and nilpotent singular support}
Finally, after restricting to nilpotent singular support, we identify categorical Frobenius traces with and without imposing the nilpotent condition.

\begin{theorem}[Trace comparison under nilpotent support] \label{thm:intro:trace}
See Theorem~\ref{thm:trace-nilp-equality}.
\end{theorem}

\input{thm_trace-nilp-equality.tex}

\section{Applications and compatibilities}\label{sec:applications}
We sketch several consequences and compatibilities that follow formally from the above results.

\subsection{Hecke dynamics, support, and conservativity}
For a tempered object $\cF\in\Shv_{\Nilp}(\Bun_G)_{\mathrm{temp}}$, Theorem~\ref{thm:hecke-orbit-support} identifies the scheme-theoretic support of $\mathsf L^{\restr}_{G,\coarse}(\cF)$ with the support generated by the $\mathrm{Hecke}_{\mathrm{fact}}(G)$-orbit of $\cF$. In particular, if a function $f\in\Gamma(\LS^{\restr}_{\check G},\mathcal O)$ acts nilpotently on the Hecke orbit, then its restriction to $\operatorname{Supp}_{\check G}\big(\mathsf L^{\restr}_{G,\coarse}(\cF)\big)$ vanishes, and conversely. The conservativity statement in Theorem~\ref{thm:hecke-orbit-support} then follows, ensuring that $\mathsf L^{\restr}_{G,\coarse}$ detects isomorphisms between tempered objects.

\subsection{Eisenstein series in families and base change}
By Theorem~\ref{thm:parabolic-zastava-flatness}, the parabolic Zastava kernel $j_!(\boldsymbol e)$ is $R_0$-flat and ULA in families. Therefore, for any ULA object $\mathcal F\in\Shv(\Bun_{M,R_0})$, the formation of $\mathrm{Eis}^-_{!}(\mathcal F)$ commutes with specialization to $K$ and $k$. The Whittaker coefficient identity in Theorem~\ref{thm:parabolic-zastava-flatness} (vacuum coefficient after translation by $\rho_P(\omega_X)$) identifies the specialized Eisenstein series with the action of the factorization object $\mathrm{Fact}(\Omega_{\mathrm{loc}})$ on the specialized Levi datum.

\subsection{QCoh specialization and Whittaker coefficients}
The QCoh-level formula in Theorem~\ref{thm:spectral-specialization} produces a canonical isomorphism
\[
\mathsf L^{\restr}_{G,k,\coarse}\big(\Sp_{K\to k}(\cF)\big)
\simeq
\omega\otimes^{\mathbb L}\underline{\operatorname{Hom}}\Big(\Poinc^{!}_{\Vac,\spec,k},\,\Sp^{\IndCoh}_{K\to k}\,\mathsf L^{\restr}_{G,K}(\cF)\Big),
\]
compatible with Hecke and Eisenstein functors. Applying global sections recovers the Whittaker coefficient identity for $\coeff^{\Vac}_{G,k}\big(\Sp_{K\to k}(\cF)\big)$.

\subsection{Specialization of spectral support}
Proposition~\ref{prop:supp-specialization} shows that for $E\in\IndCoh\big(\LS^{\restr}_{\check G,K}\big)$, the spectral support specializes schematically: the support of $\Sp^{\IndCoh}_{K\to k}(E)$ equals the schematic specialization of $\operatorname{Supp}_{\check G}(E)$ along $\LS^{\restr}_{\check G,K}\to\LS^{\restr}_{\check G,k}$. This provides a geometric control on supports and is used in the proof of Theorem~\ref{thm:spectral-specialization}.

\subsection{Frobenius traces}
When $k=\mathbb F_q$, Theorem~\ref{thm:trace-nilp-equality} identifies the categorical Frobenius traces computed in $\IndCoh$ and in the nilpotent-singu\-lar-support subcategory $\IndCoh_{\Nilp}$, uniformly over unions of connected components in $\LS^{\restr}_{\\check G}$. For compact automorphic objects $\cF$, this implies equality of Grothendieck--Lefschetz trace distributions for the coarse and the refined Langlands functors.

\section{Related work}\label{sec:related}
Our use of nilpotent singular support on the spectral side traces back to the foundational work of Arinkin and Gaitsgory \cite{ArinkinGaitsgory2015-SingularSupport}, where singular support for coherent sheaves on quasi-smooth derived stacks is developed and the categorical geometric Langlands conjecture is formulated in this language. % Sources: citeturn0search4turn0search2turn0search5

The Eisenstein series functors and the geometry of Drinfeld compactifications play a central role in our analysis of parabolic Zastava kernels. We rely on the geometric Eisenstein framework of Braverman--Gaitsgory \cite{BravermanGaitsgory2002-GeometricEisenstein} and the intersection cohomology of Drinfeld's compactifications by Braverman--Finkelberg--Gaitsgory--Mirkovi\'c \cite{BFGM2002-ICDrinfeld}. % Sources: citeturn0search8turn0search9turn0search10turn0search3turn0search6

The stack of local systems with restricted variation $\LS^{\restr}_{\check G}$ and the restricted form of the conjecture provide the natural home for our coarse specialization statements. We refer to Arinkin--Gaitsgory--Kazhdan--Raskin--Rozenblyum--Varshavsky \cite{AGKRRV2020-RestrictedLocSys} for the construction and for the compatibility of the restricted framework with nilpotent singular support and Hecke operations. % Sources: citeturn2search0turn2search1

Finally, our compatibilities with Hecke, Eisenstein, and the QCoh-valued realization of the coarse functor fit naturally with the recent series toward the proof of geometric Langlands in characteristic zero. In particular, the construction of the global Langlands functor and its structural properties in \cite{GaitsgoryRaskin2024-GLFunctorI} contextualize our coarse specialization results and Hecke-orbit control within a broader strategy. % Sources: citeturn1search0turn1search1turn1search5

\section{Proof strategy and interdependence of results}\label{sec:strategy}
We briefly indicate how the statements interact; full proofs appear in the companion files.

\subsection*{From Zastava flatness to QCoh specialization}
The $R_0$-flatness and ULA property of the parabolic Zastava kernel (Theorem~\ref{thm:parabolic-zastava-flatness}) imply base-change compatibility for $\mathrm{Eis}^-_{!}$ and control the formation of Whittaker coefficients in families. These feed into the QCoh-level spectral specialization (Theorem~\ref{thm:spectral-specialization}) by comparing geometric Eisenstein on the automorphic side with tensorial operations on $\QCoh(\LS^{\restr}_{\check G})$.

\subsection*{Hecke orbits and supports}
The Hecke-orbit description of spectral support for tempered objects (Theorem~\ref{thm:hecke-orbit-support}) combines with the specialization-of-supports Proposition~\ref{prop:supp-specialization} to propagate support control from $K$ to $k$. This leads to conservativity of the coarse functor on tempered objects and to the commutative square in Theorem~\ref{thm:langlands-specialization}.

\subsection*{Mixed characteristic essential surjectivity}
The essential surjectivity of $\Sp^{\IndCoh}_{K\to k}$ in mixed characteristic (Theorem~\ref{thm:langlands-specialization}) is proved by a deformation/approximation argument on $\IndCoh_{\Nilp}(\LS^{\restr}_{\check G,(-)})$, using nilpotent-singular-support control and schematic specialization of supports (Proposition~\ref{prop:supp-specialization}).

\subsection*{Trace comparison}
The trace comparison (Theorem~\ref{thm:trace-nilp-equality}) relies on the identification of the coarse and refined spectral images on nilpotent supports and on a devissage over connected components of $\LS^{\restr}_{\check G}$, culminating in equality of categorical Frobenius traces.

\section{Conclusion}
We have established a package of specialization and compatibility results that tie together Hecke dynamics, parabolic Eisenstein geometry, and the coarse QCoh-valued spectral functor in the restricted setting. The results clarify how automorphic operations and spectral supports behave in families and across characteristics, providing structural input toward a robust, functorial, and trace-compatible form of geometric Langlands that interacts well with both nilpotent singular support and Whittaker coefficients.

\section*{Acknowledgments}
We thank the authors of \cite{ArinkinGaitsgory2015-SingularSupport,AGKRRV2020-RestrictedLocSys,BravermanGaitsgory2002-GeometricEisenstein,BFGM2002-ICDrinfeld,GaitsgoryRaskin2024-GLFunctorI} for foundational contributions on which this work builds.

\section*{Bibliography}
\input{bib.tex}

\end{document}
