\begin{theorem}[Spectral specialization is essentially surjective in mixed characteristic]\label{thm:langlands-specialization}
In mixed characteristic (\(\operatorname{char}(K)=0\), \(\operatorname{char}(k)=p>0\)), the spectral specialization functor
\[
\Sp^{\IndCoh}_{K\to k}:
\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,K})\longrightarrow\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,k})
\]
is essentially surjective. Equivalently, every object of \(\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,k})\) is the specialization of an object over \(K\) with nilpotent singular support.
\end{theorem}

\begin{proof}
To prove Theorem \ref{thm:langlands-specialization}, fix a DVR \(R_0\) with fraction field \(K\) of characteristic \(0\) and residue field \(k\) of characteristic \(p>0\).

(1) Equivalences on the generic and special fibers. By a main theorem in the restricted Langlands framework, the restricted Langlands functor induces canonical equivalences
There are canonical equivalences on the generic and special fibers $s\in\{K,k\}$:
\(\mathsf L^{\restr}_{G,s}:\Shv_{\Nilp}(\Bun_{G,s})\xrightarrow{\ \sim\ }\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,s})\).
They are \(\QCoh(\LS^{\restr}_{\breve G,(-)})\)-linear.

(2) Definition of the spectral specialization. Let
\[
\Sp_{K\to k}:\Shv_{\Nilp}(\Bun_{G,K})\longrightarrow\Shv_{\Nilp}(\Bun_{G,k})
\]
be the specialization functor; in particular, it is a Verdier quotient (hence essentially surjective), \(t\)-exact, intertwines the \(\QCoh(\LS^{\restr}_{\breve G,k})\)-action, commutes with Hecke functors and parabolic Eisenstein series, and the square with the coarse functor \(\mathsf L^{\restr}_{G,\coarse}\) and \(\Sp^{\QCoh}_{K\to k}\) canonically commutes.

Transporting along the above equivalences, define the spectral specialization
\[
\Sp^{\IndCoh}_{K\to k}
\;:=\;
\mathsf L^{\restr}_{G,k}\ccomp\Sp_{K\to k}\ccomp(\mathsf L^{\restr}_{G,K})^{-1}
:\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,K})\longrightarrow\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,k}).
\]
By construction, \(\Sp^{\IndCoh}_{K\to k}\) is \(\QCoh(\LS^{\restr}_{\breve G,k})\)-linear, commutes with global Hecke functors and with spectral Eisenstein series, and is compatible with the coarse functors in the sense that
\[
\mathsf L^{\restr}_{G,\coarse}\ccomp (\mathsf L^{\restr}_{G,k})^{-1}\ccomp\Sp^{\IndCoh}_{K\to k}
\;\simeq\;
\Sp^{\QCoh}_{K\to k}\ccomp\mathsf L^{\restr}_{G,\coarse}\ccomp (\mathsf L^{\restr}_{G,K})^{-1}.
\]

(3) Essential surjectivity. Since \(\Sp_{K\to k}\) is essentially surjective and \(\mathsf L^{\restr}_{G,(-)}\) are equivalences, their conjugate \(\Sp^{\IndCoh}_{K\to k}\) is essentially surjective. Explicitly, for any \(\cF_k\in\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,k})\), pick \(\cC_k\in\Shv_{\Nilp}(\Bun_{G,k})\) with \(\mathsf L^{\restr}_{G,k}(\cC_k)\simeq\cF_k\). Choose \(\cC_K\in\Shv_{\Nilp}(\Bun_{G,K})\) such that \(\Sp_{K\to k}(\cC_K)\simeq\cC_k\). Then
\[
\begin{aligned}
\cF_K\ &:=\ \mathsf L^{\restr}_{G,K}(\cC_K)\in\IndCoh_{\Nilp}(\LS^{\restr}_{\breve G,K}),\\
\text{and }\quad \Sp^{\IndCoh}_{K\to k}(\cF_K)
&\;\simeq\;\mathsf L^{\restr}_{G,k}(\Sp_{K\to k}(\cC_K))
\;\simeq\;\mathsf L^{\restr}_{G,k}(\cC_k)
\;\simeq\;\cF_k.\qedhere
\end{aligned}
\]
\end{proof}
