% Auto-generated bibliography (sanitized)
\begin{thebibliography}{99}
\bibitem{Topkis1998} Topkis, D. M. Supermodularity and Complementarity. Princeton University Press, 1998. \url{https://press.princeton.edu/books/hardcover/9780691058649/supermodularity-and-complementarity}
\bibitem{KleinbergMullainathanRaghavan2017} Kleinberg, J., Mullainathan, S., and Raghavan, M. Inherent trade-offs in the fair determination of risk scores. arXiv:1609.05807, 2016. \url{https://arxiv.org/abs/1609.05807}
\bibitem{BenDavidEtAl2010} Ben-David, S., Blitzer, J., Crammer, K., Kulesza, A., Pereira, F., and Wortman Vaughan, J. A theory of learning from different domains. Machine Learning 79(1):151--175, 2010. \url{https://doi.org/10.1007/s10994-009-5152-4}
\bibitem{VanderWeele2015} VanderWeele, T. J. Explanation in Causal Inference: Methods for Mediation and Interaction. Oxford University Press, 2015. \url{https://doi.org/10.1093/acprof:oso/9780199325870.001.0001}
\bibitem{EsfahaniKuhn2018} Mohajerin Esfahani, P. and Kuhn, D. Data-driven distributionally robust optimization using the Wasserstein metric: performance guarantees and tractable reformulations. Mathematical Programming 171(1):115--166, 2018. \url{https://doi.org/10.1007/s10107-017-1171-1}
\bibitem{LebrikizumabTREBLE2018} Simpson, E. L., Flohr, C., Eichenfield, L. F., Bieber, T., Sofen, H., Taieb, A., Paul, C., Cork, M., Thyssen, J. P., Silverberg, J. I., et al. Efficacy and safety of lebrikizumab (an anti-IL-13 monoclonal antibody) in adults with moderate-to-severe atopic dermatitis inadequately controlled by topical corticosteroids: a randomized, placebo-controlled phase II trial (TREBLE). Journal of the American Academy of Dermatology 78(5):863--871, 2018. \url{https://doi.org/10.1016/j.jaad.2018.01.017}
\bibitem{LebrikizumabJAMA2020} Guttman-Yassky, E., Blauvelt, A., Eichenfield, L. F., Paller, A. S., Armstrong, A. W., et al. Efficacy and Safety of Lebrikizumab, a High-Affinity Interleukin 13 Inhibitor, in Adults With Moderate to Severe Atopic Dermatitis. JAMA Dermatology 156(4):411--420, 2020. \url{https://doi.org/10.1001/jamadermatol.2020.0079}
\bibitem{TralokinumabBJD2020} Wollenberg, A., Beck, L. A., Blauvelt, A., Simpson, E. L., Chen, Z., Ballal, S., et al. Tralokinumab for atopic dermatitis: a promising new therapy. British Journal of Dermatology 183(5):740--741, 2020. \url{https://doi.org/10.1111/bjd.19699}
\bibitem{TralokinumabECZTRA12BJD2021} Silverberg, J. I., Toth, D., Bieber, T., Alexis, A. F., Elewski, B. E., Pink, A. E., et al. Tralokinumab for moderate-to-severe atopic dermatitis: results from two 52-week, randomized, double-blind, multicentre, placebo-controlled phase III trials (ECZTRA 1 and ECZTRA 2). British Journal of Dermatology 184(3):437--449, 2021. \url{https://doi.org/10.1111/bjd.19574}
\bibitem{TralokinumabECZTRA3BJD2021} Wollenberg, A., Blauvelt, A., Guttman-Yassky, E., Worm, M., Lynde, C., Lacour, J.-P., et al. Tralokinumab plus topical corticosteroids for the treatment of moderate-to-severe atopic dermatitis: results from the double-blind, randomized, multicentre, placebo-controlled phase III ECZTRA 3 trial. British Journal of Dermatology 184(3):450--463, 2021. \url{https://doi.org/10.1111/bjd.19573}
\bibitem{StaphInADChapter2008} Hoeger, P. H., Lenz, W. Role of \textit{Staphylococcus aureus} in atopic dermatitis. In: Textbook of Atopic Dermatitis. 2008. \url{https://doi.org/10.3109/9780203091449-9}
\bibitem{SimpsonNEJM2016} Simpson, E. L., Bieber, T., Guttman-Yassky, E., Beck, L. A., Blauvelt, A., Cork, M. J., Silverberg, J. I., Deleuran, M., Kataoka, Y., Lacour, J.-P., Kingo, K., Worm, M., Poulin, Y., Wollenberg, A., Soo, Y., Graham, N. M. H., Pirozzi, G., Akinlade, B., Staudinger, H., Mastey, V., Eckert, L., Gadkari, A., Stahl, N., Yancopoulos, G. D., and Ardeleanu, M. Two Phase 3 Trials of Dupilumab versus Placebo in Atopic Dermatitis. New England Journal of Medicine, 375(24):2335--2348, 2016. \url{https://doi.org/10.1056/NEJMoa1610020}
\bibitem{FezakinumabJAAD2018} Guttman-Yassky, E., Brunner, P. M., Neumann, A. U., Khattri, S., Pavel, A. B., Malik, K., Singer, G. K., Baum, D., Gilleaudeau, P., Sullivan-Whalen, M., Misiak-Tlosta, M., Estrada, Y. D., Champhekar, A., Maari, C., Dumont, N., and Krueger, J. G. Efficacy and safety of fezakinumab (an IL-22 monoclonal antibody) in adults with moderate-to-severe atopic dermatitis inadequately controlled by conventional treatments: a randomized, double-blind, phase 2a trial. Journal of the American Academy of Dermatology 78(5):872--881, 2018. \url{https://doi.org/10.1016/j.jaad.2018.01.016}
\bibitem{DatasetShift2008} Quionero-Candela, J., Sugiyama, M., Schwaighofer, A., and Lawrence, N. D. (eds.). Dataset Shift in Machine Learning. MIT Press, 2008. \url{https://doi.org/10.7551/mitpress/9780262170055.001.0001}
\bibitem{ArjovskyIRM2019} Arjovsky, M., Bottou, L., Gulrajani, I., and Lopez-Paz, D. Invariant Risk Minimization. arXiv:1907.02893, 2019. \url{https://arxiv.org/abs/1907.02893}
\bibitem{HardtEquality2016} Hardt, M., Price, E., and Srebro, N. Equality of Opportunity in Supervised Learning. arXiv:1610.02413, 2016. \url{https://arxiv.org/abs/1610.02413}
\bibitem{HuangBleach2011} Huang, J. T., Abrams, M., Tlougan, B., Rademaker, A., and Paller, A. S. Dilute bleach baths for Staphylococcus aureus colonization in atopic dermatitis to decrease disease severity. Archives of Dermatology 147(2):246--253, 2011. \url{https://doi.org/10.1001/archdermatol.2010.434}
\end{thebibliography}
